---
title: "Advanced Clustering"
author: "Adam Shelton"
date: "11/11/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(here)
library(cluster)
library(FactoMineR)
library(factoextra)
library(NbClust)
library(dbscan)
library(cowplot)
library(skimr)
library(ggcorrplot)
library(missMDA)
library(cluster)
library(missForest)
library(tictoc)
library(doParallel)

knitr::opts_chunk$set(echo = TRUE, fig.height = 6, fig.width = 8, dpi = 400)

set.seed(60615)
```

## Import Data
```{r data}
original_data = read_csv(here("Data", "final_okcupid.csv")) %>% select(-c("new_index", "orig_index", "clean_text", "essay9", "long_words", "flesch",  "dbscan_cluster", "profile_length", "prop_longwords" ))

names(original_data)
```

## Descriptive Statistics
```{r descr-stats, cache=TRUE, fig.height = 8, fig.width = 11,}
skim_list = original_data %>% skim() %>% partition()

skim_list$numeric %>% kable()
skim_list$character%>% kable()

original_data %>% mutate_if(is.character, factor) %>% mutate_all(as.numeric) %>% cor(use = "pairwise.complete.obs") %>% ggcorrplot()

clusterability = original_data %>% mutate_if(is.character, factor) %>% mutate_all(as.numeric) %>% sample_n(5000) %>% get_clust_tendency(n = 50)
clusterability$hopkins_stat
clusterability$plot
```


## PCA
```{r pca, cache=TRUE}
original_data %>% mutate_if(is.character, factor) %>% mutate_all(as.numeric) %>% mutate_all(scale) %>% PCA(graph = FALSE) %>% fviz_pca_biplot(label = "var", col.var = "red", col.ind = "grey")
ggsave2(here("Clustering", "pca_v2.png"), height = 7, width = 11)
```

## Agglomerative Nesting
```{r agg-nest, error=TRUE, cache=TRUE}
sampled_data = original_data %>% sample_n(5000) 
agnes_data = sampled_data %>% mutate_if(is.character, factor) %>% mutate_all(as.numeric) %>% mutate_all(scale) 
agnes_diss = agnes_data %>% as.matrix() %>% daisy(metric = "gower")
nb_results = NbClust(data = agnes_data, diss = agnes_diss, distance = NULL, min.nc = 2, max.nc = 10, method = "ward.D2")

fviz_nbclust(nb_results)

agnes_mod = agnes_diss %>% hcut(isdiss = TRUE, k = 2, hc_func = "agnes", hc_method = "ward.D2")
fviz_dend(agnes_mod)
sampled_data$cluster = agnes_mod$cluster
fviz_cluster(agnes_mod, data = agnes_diss, labelsize = 0)

saveRDS(sampled_data, here("Data", "Results", "agnes_results.rds"))
write_csv(sampled_data, here("Data", "Results", "agnes_results.csv"))
```

### Cluster Interpretation
```{r clust-inter}
modal = function(vect, percent = FALSE, only_one = FALSE) {
  library(tidyverse)
  modal_val = vect %>% unlist() %>% table() %>% .[. == max(.)] %>% names()
  if (only_one) {
    modal_val = modal_val[1]
  }
  if (percent) {
    return(vect %>% unlist() %>% .[. == modal_val] %>% (function(x) length(x) / length(vect)))
    }
  modal_val
}

cluster_significance = function(var, data, clus_var = "cluster") {
  wilcox.test(as.formula(paste(var, "~", clus_var)), data)$p.value
}

sampled_data %>% select_if(is.numeric) %>% group_by(cluster) %>% summarise_all(mean) %>% kable(caption = "Mean by Cluster")

sampled_data %>% select_if(is.numeric) %>%  {sapply(names(select(., -cluster)), cluster_significance, data = .)} %>% round(3) %>% enframe() %>% kable(caption = "Wilcox Test P-values")

sampled_data %>% select_if(is.numeric) %>% group_by(cluster) %>% group_by(cluster) %>% summarise_all(sd) %>% kable(caption = "Standard Deviation by Cluster")

sampled_data %>% select_if(is.numeric) %>% group_by(cluster) %>% group_by(cluster) %>% summarise_all(median) %>% kable(caption = "Median by Cluster")

sampled_data %>% mutate(cluster = factor(cluster)) %>% select_if((function(x) !is.numeric(x))) %>% group_by(cluster) %>% summarise_all(modal, only_one = TRUE) %>% kable(caption = "Mode by Cluster")
sampled_data %>% mutate(cluster = factor(cluster)) %>% select_if((function(x) !is.numeric(x))) %>% group_by(cluster) %>% summarise_all(modal, percent = TRUE, only_one = TRUE) %>% mutate_if(is.numeric, round, 3) %>% kable(caption = "Mode by Cluster")

