---
title: "DBSCAN on Doc2Vec Results"
author: "Adam Shelton"
date: "12/2/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(here)
library(cluster)
library(FactoMineR)
library(factoextra)
library(NbClust)
library(dbscan)
library(cowplot)
library(skimr)
library(ggcorrplot)

knitr::opts_chunk$set(echo = TRUE, fig.height = 6, fig.width = 8, dpi = 400)

set.seed(60615)
```

## About the Data
```{r data}
doc2vec_data = read_csv(here("Data", "doc2vec_results.csv"))
doc2vec_data %>% skim() %>% partition() %>% .$numeric %>% kable()
doc2vec_data %>% select(-X1) %>% {ggcorrplot(cor(.), p.mat = cor_pmat(.), hc.order = TRUE, insig = "blank")}
```

## Clusterability
```{r clusterability}
clusterability = doc2vec_data %>% select(-X1) %>% get_clust_tendency(n = 50)
#clusterability$plot
```

The Doc2Vec data has a Hopkins Statistic of `r round(clusterability$hopkins_stat, 3)`.

## Identifying Outliers with DBSCAN

### Building a DBSCAN Model
```{r dbscan}
doc2vec_data %>% select(-X1) %>% kNNdistplot(k = 5)
dbscan_mod = doc2vec_data %>% select(-X1) %>% dbscan(16, 5)
doc2vec_data %>% select(-X1) %>% {fviz_cluster(dbscan_mod, data = .)}

dbscan_results = doc2vec_data %>% bind_cols(enframe(dbscan_mod$cluster, name = NULL, value = "cluster"))
read_csv(here("Data", "compressed_with_results.csv")) %>% mutate(dbscan_cluster = dbscan_mod$cluster) %>% write_csv(here("Data", "compressed_with_results.csv"))
```

The DBSCAN model identified `r sum(dbscan_mod$cluster == 0)` outliers, `r round(sum(dbscan_mod$cluster == 0) / length(dbscan_mod$cluster) * 100, 2)`% of the observations in the Doc2Vec results.

### Interpreting Outliers
```{r merge}
merged_demo_data = read_csv(here("Data", "compressed_okcupid.csv")) %>% select(-essay0, -essay9) %>% bind_cols(select(dbscan_results, cluster))
merged_doc2vec_data = read_csv(here("Data", "compressed_okcupid.csv")) %>% select(X1, essay0, essay9) %>% bind_cols(select(dbscan_results, -X1))
```

#### Demographic Data
```{r demo-data}
modal = function(vect, percent = FALSE) {
  library(tidyverse)
  modal_val = vect %>% unlist() %>% table() %>% .[. == max(.)] %>% names()
  if (percent) {
    return(vect %>% unlist() %>% .[. == modal_val] %>% (function(x) length(x) / length(vect)))
    }
  modal_val
}

merged_demo_data %>% select(-c(X1, education)) %>% select_if(is.numeric) %>% group_by(cluster) %>% summarise_all(mean) %>% kable(caption = "Mean by Cluster")
merged_demo_data %>% select(-c(X1, education)) %>% select_if(is.numeric) %>% group_by(cluster) %>% group_by(cluster) %>% summarise_all(sd) %>% kable(caption = "Standard Deviation by Cluster")
merged_demo_data %>% select(-c(X1, education)) %>% select_if(is.numeric) %>% group_by(cluster) %>% group_by(cluster) %>% summarise_all(median) %>% kable(caption = "Median by Cluster")

merged_demo_data %>% select(-c(X1, education)) %>% mutate(cluster = factor(cluster)) %>% select_if((function(x) !is.numeric(x))) %>% group_by(cluster) %>% summarise_all(modal) %>% kable(caption = "Mode by Cluster")
merged_demo_data %>% select(-c(X1, education)) %>% mutate(cluster = factor(cluster)) %>% select_if((function(x) !is.numeric(x))) %>% group_by(cluster) %>% summarise_all(modal, percent = TRUE) %>% mutate_if(is.numeric, round, 3) %>% kable(caption = "Mode by Cluster")
```


#### Doc2Vec Data
```{r interpret-outliers}
dbscan_results %>% select(-X1) %>% group_by(cluster) %>% summarise_all(mean) %>% kable(caption = "Mean by Cluster")
dbscan_results %>% select(-X1) %>% group_by(cluster) %>% summarise_all(sd) %>% kable(caption = "Standard Deviation by Cluster")
dbscan_results %>% select(-X1) %>% group_by(cluster) %>% summarise_all(median) %>% kable(caption = "Median by Cluster")
```

### Profile Differences
```{r profile-diff}
merged_doc2vec_data %>% select(cluster, essay0) %>% group_by(cluster) %>% sample_n(25) %>% kable()
```

