---
title: "stm-okcupid-demo+dbscan"
author: "Li Liu"
date: "December 10, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stm)
library(quanteda)
library(topicmodels)
library(tidytext)
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(tm)
library(grid)
library(wordcloud)
library(wordcloud2)
library(tidyverse)
library(igraph)
library(stmCorrViz)
```

## Read in data
```{r data, echo=FALSE}
setwd('C:/Users/lliu9/Desktop/UML_Project/unsupervised-dating/Data')
#cleaned okcupid data
data <- read_csv("final_okcupid.csv")

#data <- sample_n(essay, 100)
data <- data[c('clean_text', 'fit', 'edu', 'height_group', 'race_ethnicity', 'dbscan_cluster')]
```

## Clean the data
```{r clean}
processed <- textProcessor(data$clean_text, metadata = data)
out <- prepDocuments(processed$documents, processed$vocab,
                     processed$meta, lower.thresh = 0)
docs <- out$documents
vocab <- out$vocab
meta <-out$meta
```


## Fit the STM
```{r stm}
Fit <- stm(documents = out$documents, vocab = out$vocab,
                       K = 9, prevalence =~ fit + edu + height_group + race_ethnicity+dbscan_cluster,
                       max.em.its = 50, data = out$meta,
                       init.type = "Spectral", verbose=FALSE)
```

## Topics
```{r label}
labelTopics(Fit, c(1:9))
```


## Estimating metadata/topic relationships
```{r estimate}
prep <- estimateEffect( ~ fit + edu + height_group + race_ethnicity + dbscan_cluster, Fit,
                         meta = out$meta, uncertainty = "Global")
```


## Estimates a regression where documents are the units, the outcome is the proportion of each document about a topic in an STM model and the covariates are document-meta data.
```{r print}
for (i in seq(1:9)){
    print(summary(prep, topic=i))}
```


## Graphical display of estimated topic proportions
```{r summary}
#jpeg('toptopics.jpeg')
plot(Fit, type = "summary", xlim = c(0, .3))
#dev.off
```

## The most frequent words in the model such as for top topics

```{r labels}
jpeg('top3topics.jpeg')
plot(Fit, type="labels", topics=c(5,4,7))
dev.off()
```

## The most frequent words in the model such as for bottom topics
```{r labels2}
jpeg('bottom3topics.jpeg')
plot(Fit, type="labels", topics=c(1,2,9))
dev.off()
```

## The histograms of topics
```{r hist}
jpeg('hist.jpeg')
plot(Fit, type="hist")
dev.off()
```

## A comparison of two topics
```{r perspectives}
jpeg('comparison.jpeg')
plot(Fit, type="perspectives", topics=c(6,8 ))
dev.off()

```


```{r quality}
jpeg('topicQuality.jpeg')
topicQuality(model=Fit, documents=docs)
dev.off()
```



```{r word-cloud}
cloud(Fit, topic = 1)
```

## Word cloud display
```{r cloud}
for (i in seq(1:9)){
    name <- paste('topic', str(i), '.jpg', sep='')
    jpeg(name)
    cloud(Fit, topic = i, scale = c(4,0.2) )
    dev.off}
```

## Network
```{r network}
# Positive correlations between topics indicate that both topics are likely to be discussed within a document.
mod.out.corr <- topicCorr(Fit)
# Graphical display of topic correlations.
jpeg('network.jpeg')
plot(mod.out.corr)
dev.off()
```
